|

### 2022-03-11 Memo/Memo_Template.Rmd
up
Elaborando o memorandum e adicionando trechos em negrito no artigo.

---
title: "Dinner"
to: Ralf
from: Martin
date: "`r Sys.time()`"
output: 
  pdf_document:
    template: article-template.latex
logo: "\\includegraphics[width=.25\\textwidth]{unnamed.png}"

@@

\section{Suggestions Raised by Reviewer 1}
\begin{itemize}
\item \textit{Overall the literature review is strong. I would recommend a couple of additions. Include among them is an important work the authors should cite on legislative size and spending and that is Gilligan and Matsusaka's 2001 article entitled ""Fiscal Policy, Legislature Size, and Political Parties: Evidence from the First Half of the Twentieth Century." Their findings are relevant for this study and should be referenced. In addition, the recently published book Population and Politics: The Impact of Scale by Gerring and Veenendaal which has a comprehensive analysis of this topic should also be incorporated into the literature review.\ldots }

\vspace{.2cm}
We thank the reviewer 1 for these two relevant additions. \textbf{We cite Gilligan and Matsusaka's 2001 article on page XXX:}: XXXX. \textbf{The Gerring and Veenendaal's book citation is on page XXX:} XXX. 
\vspace{.5cm}

@@

We agree with R1 that needed to provide more information on the online survey. Therefore, we detailed our procedures in the \textbf{Appendix Section XXX}.

@@

\vspace{.2cm}
\textbf{We now show the analysis without the dummy variable (page XXX) for the northeast region in the main paper and move the regressions with the dummy to the Appendix (page XXX).} The results are virtually the same. We agree with R1 that the inclusion of the dummy variable might generate unecessary confusion and are not central to our argument. \textbf{Therefore, we also explain on page XXX why we included the dummy variable for the northeast region on page XXX}: XXX.

@@

\end{itemize}
\section{Suggestions Raised by Reviewer 2}
\begin{itemize}
\item \textit{One minor issue for the author(s) to consider in future research: on p. 14 the paper states, "On average, municipal taxes account for only 5\% of the local budgets, while mandatory transfers from state and federal governments correspond to the remaining 95\%. This reduces the ability of municipal legislators to effectively increase local spending, which makes improvements in local services dependent only on the composition of their local investments." There is an alternative mechanism that the author(s) has not considered and that has been shown to work in resource allocations to municipalities in Japan under similar circumstances. A recent paper by Amy Catalinac, Bruce Bueno de Mesquita and Alastair Smith tests a formal model in which variance in centrally-provided local municipality resources is a function of a tournament among municipalities within a larger legislative district ("A Tournament Theory of Pork Barrel Politics: The Case of Japan" Comparative Political Studies 2020). Perhaps future research might compare the impact of the tournament structure with the local city council effects in Brazil as studied here.}

\vspace{.2cm}
We incorporate the suggestion for future research in the conclusion: XXX \textbf{(page XXX)}. We also agree with R2 that the testing of the proposed mechanism is an extremelly interesting project for a follow-up article.

@@

\vspace{.2cm}
We collapse two paragraphs from R3 since they speak to core topics in our paper, such as the allocation of the resources and polarization. First, \textbf{in the Appendix,} page XXX, we show that an extra-legislator does not increase the municipal spending significantly. Therefore, our results speaks more about the allocation of resources than on public spending. Also, \textbf{in the Appendix, page XX,} we show that the mayors' party and the representativeness of the extra legislator is not driving the results. Unfortunately.

@@

\vspace{.2cm}
We acknowledge that the external valitidy of our findings might be conditional on the time period of our study, since Frye (XXX) finds... We also mention that, unlikely many papers in the literature, we cannot corroborate the assertion that one extra legislator increases public spending, representativeness, and corruption. See the relevant passages on pages XXX.

>>>>

---
title: 
to:
from: 
date: "`r Sys.time()`"
output: 
  pdf_document:
    template: article-template.latex
bibliography: references.bib

@@

\section{Suggestions Raised by Reviewer 1}
\begin{itemize}
\item \textit{Overall the literature review is strong. I would recommend a couple of additions. Include among them is an important work the authors should cite on legislative size and spending and that is \citet{GilliganMatsusaka2001} article entitled "Fiscal Policy, Legislature Size, and Political Parties: Evidence from the First Half of the Twentieth Century." Their findings are relevant for this study and should be referenced. In addition, the recently published book Population and Politics: The Impact of Scale by Gerring and Veenendaal which has a comprehensive analysis of this topic should also be incorporated into the literature review.}

\vspace{.2cm}
We thank the reviewer 1 for these two relevant additions. We cite \citet{GilliganMatsusaka2001} article \textbf{on page 7:} "Yet, \citet{GilliganMatsusaka2001} finds that in the US legislature size is associated primarily with higher spending on geographically concentrated benefits, such as education and highways."   The Population and Politics book citation is \textbf{on page 6:} "However, legislature size does not \textit{necessarily} assure representativeness" \citep[p. 85]{gerring2020population}.

@@

We agree with R1 that needed to provide more information on the online survey. Therefore, we detailed our procedures in the \textbf{Appendix Section A.14, on pages 22-23}. We also reference it \textbf{on pages 17 and 22 (footnote 13)} in the main article.

@@

\vspace{.2cm}
\textbf{We now show the analysis without the dummy variable (page XXX) for the northeast region in the main paper and move the regressions with the dummy to the Appendix (page XXX).} The results are virtually the same. We agree with R1 that the inclusion of the dummy variable might generate unecessary confusion and are not central to our argument. \textbf{Therefore, we also explain on page XXX why we included the dummy variable for the northeast region on page XXX}: XXX. Gilligan and Matsusaka.

@@

\end{itemize}
\section{Suggestions Raised by Reviewer 2}
\begin{itemize}
\item \textit{One minor issue for the author(s) to consider in future research: on p. 14 the paper states, "On average, municipal taxes account for only 5\% of the local budgets, while mandatory transfers from state and federal governments correspond to the remaining 95\%. This reduces the ability of municipal legislators to effectively increase local spending, which makes improvements in local services dependent only on the composition of their local investments." There is an alternative mechanism that the author(s) has not considered and that has been shown to work in resource allocations to municipalities in Japan under similar circumstances. A recent paper by \citet{catalinac2020tournament} tests a formal model in which variance in centrally-provided local municipality resources is a function of a tournament among municipalities within a larger legislative district. Perhaps future research might compare the impact of the tournament structure with the local city council effects in Brazil as studied here.}

\vspace{.2cm}
We agree with R2 that the testing of the proposed mechanism is an extremelly interesting project for a follow-up article. In our \textbf{conclusion, on page 27,} we write: "Future research should also evaluate whether an extra-legislator is helping the mayor in her competition for state or federal transfers, as proposed by \citet{catalinac2020tournament}."

@@

\vspace{.2cm}
We collapse two paragraphs from R3 since they speak to core topics in our paper. \textbf{In the Appendix Table XXX, on page XXX,} we show that an extra-legislator usually does not increase the municipal spending significantly. Therefore, our results speak more about the allocation of resources than on public spending. \textbf{On page 15, in the Background on the Brazilian Case Section,} we clarify why increasing the city council size usually results in a pro-mayor legislator. "Additionally, Brazil's formula for apportioning legislative seats (a combination of the Hara quota and the D'Hondt method) is an obstacle to small parties or coalitions attaining the electoral quotient that might give them a legislative seat. As a result, they often ally with larger coalitions so that they can reach the electoral quotient \citep[p. 68]{Ames2001}. Being a central political figure in the municipality, often the mayor is also a member of the most voted coalition." See also \textbf{footnote 12, on page 21-22.} Unfortunately, we could not find evidence that an extra-legislator improves descriptive representation in the city council, for instance, more female or non-white legislators \textbf{(see Table 4).} Finally, \textbf{in the Appendix, on page XX,} we show that the mayors' party is not driving the results.

@@

\vspace{.2cm}
We acknowledge that the external valitidy of our findings might be conditional on the time period or related to contexto characteristics of our study. \textbf{On page 5,} we write: "\citet{frey2021legislature}, using discontinuities in city council size after the 2009 constitutional amendment that reverted the thresholds we study here, shows that changes in council size lower the support for candidates backed by the municipal mayors. Our paper reinforces the view that partisanship matters locally, even in countries with weak ideological linkage." \textbf{On page 6-7,} we acknowledge that "since the seminal paper by \citet{Weingastetal1981}, 30 papers have systematically tested the effects of legislature size on government spending. Of these papers, only \citet{lewis2019legislature} investigates its effects on welfare, showing that larger legislatures have a negative welfare effect. \citet{frey2021legislature} analyses the Brazilian case after the 2009 legislature size change and finds a null effect in service provision from 2012 to 2016. Yet, \citet{GilliganMatsusaka2001} finds that in the US legislature size is associated primarily with higher spending on geographically concentrated benefits, such as education and highways. These results suggest that the legislature size and welfare nexus needs a dedicated theoretical and empirical assessment." Additionally, \textbf{in the Discussion Section, on page 27,} we write about the implications of our findings beyond Brazil. In this paragraph, we added the following sentence: "However, as the [...]"

### 2022-03-11 article/article.Rmd
Memo
up
Elaborando o memorandum e adicionando trechos em negrito no artigo.

Third, our article also contributes to a growing literature on municipal partisan politics. Most papers in this area estimate the effects of the mayor's party on political outcomes. For instance, \citet{de2016mayoral} and \citet{gerber2011mayors} find differences in governance when comparing Democratic and Republican mayors. Specifically about Brazil, \citet{gouvea2021partisanship} shows that social policy expenditure increase with left-wing mayors. \citet{frey2020larger}, using discontinuities in city council size after the 2009 constitutional amendment that reverted the thresholds we study here, shows that changes in council size lower the support for candidates backed by the municipal mayors. Our paper reinforces the view that partisanship matters locally, even in countries with weak ideological linkage.

@@

The legislature size literature highlights that the number of legislators causes tension between representation and efficiency \citep{frederick2008people, jacobs2015explaining, muzzio1989size, rush2013conclusion, Stigler1976, taagepera1972size}. Larger legislatures improve representation as the election thresholds decrease and the ratio of population-per-politician decreases. This facilitates the electoral success of ethnic and political minorities \citep{allenrepresentation}. Conversely, the improvements in representation are countered by the decline in efficiency in larger legislatures. The enlarged size makes it harder for members to coordinate and collaborate without partisanship and legislative structures \citep{kirkland2014chamber, rush2013conclusion}. It also increases the potential number of veto players, decreasing the policymaking efficiency \citep{tsebelis2002veto}. Balancing these two incentives is crucial for the optimal legislative composition \citep{auriol2012optimal, taagepera1972size}.

However, the legislature size scholarship has overlooked two questions: first, does legislature size matter in contexts where the legislative bodies are not the pivotal decision-maker? And second, what is the ultimate effect of legislature size on welfare? On the one hand, legislature size's effects on welfare represent a significant gap in the political economy literature. It is likely generated by the predominance of the "law of 1/n" scholarship, which emphasized larger legislatures' overspending consequence. Since the seminal paper by \citet{Weingastetal1981}, 30 papers have systematically tested the effects of legislature size on government spending \citep{freire2021legislature}. Of these papers, only \citet{lewis2019legislature} investigates its effects on welfare, showing that larger legislatures have a negative welfare effect.\footnote{\citet{koppel2004public} also shows, using a repeated game where the proposal prerogative rotates in a legislature, that larger legislatures increase the chances of non-cooperative outcomes, lowering public goods provision.} \citet{frey2020larger} analyses the Brazilian case after the 2009 legislature size change and finds a null effect in service provision from 2012 to 2016. These results suggest that the legislature size and welfare nexus needs a dedicated theoretical and empirical assessment.

@@

Following the ruling of the Supreme Court, in March 2004 the Supreme Electoral Court established a series of population cutoffs for all municipal legislatures. Following the Brazilian Constitution, the Court specified that cities with up to one million residents should have between 9 and 21 legislators. The number of seats was allocated as follows. Each town starts with nine councilors, then adds one legislator for every 47,619 inhabitants until their councils reach 21 members. This threshold implies that cities with a population between 571,428 and one million should all have the same number of legislators, that is, 21 of them. Conversely, cities between one and four million inhabitants should have at least 33 councilors, and this number increases up to 41 members following the previous formula of one additional legislator per 47,619 inhabitants.

@@

We built two novel datasets to provide evidence for our mechanism. First, we ran a survey with former city councilors, asking how mayors consolidate their coalition support within the city council. Second, we collected 346,553 laws approved in 63 municipalities within ten thousand inhabitants away from the city council size thresholds. We hand-coded 3,466 laws into four categories: public goods, oversight, education and health care-related legislation, and other legislative duties. After hand-coding these laws, we used a Supporting Vector Machine (SVM) algorithm to classify the remainder laws. From all of the algorithms we tested, SVM achieved the highest performance.

@@

Municipalities work very similarly in terms of the incentives for legislative-executive bargaining. The stakes are lower, and the negotiations involve only one legislative branch. Still, in a system such as Brazil's, with more than thirty-five registered parties, mayors face substantial challenges to the support for their agendas. Having extra help in the council can tilt the bargaining towards cheaper governing, thus improving public goods provision.

>>>>

Third, our article also contributes to a growing literature on municipal partisan politics. Most papers in this area estimate the effects of the mayor's party on political outcomes. For instance, \citet{de2016mayoral} and \citet{gerber2011mayors} find differences in governance when comparing Democratic and Republican mayors. Specifically about Brazil, \citet{gouvea2021partisanship} shows that social policy expenditure increase with left-wing mayors. \citet{frey2021legislature}, using discontinuities in city council size after the 2009 constitutional amendment that reverted the thresholds we study here, shows that changes in council size lower the support for candidates backed by the municipal mayors. Our paper reinforces the view that partisanship matters locally, even in countries with weak ideological linkage.

@@

The legislature size literature highlights that the number of legislators causes tension between representation and efficiency \citep{frederick2008people, jacobs2015explaining, muzzio1989size, rush2013conclusion, Stigler1976, taagepera1972size}. Larger legislatures improve representation as the election thresholds decrease and the ratio of population-per-politician decreases. This facilitates the electoral success of ethnic and political minorities \citep{allenrepresentation}. \textbf{However, legislature size does not \textit{necessarily} assure representativeness \citep[p. 85]{gerring2020population}.} Conversely, the improvements in representation are countered by the decline in efficiency in larger legislatures. The enlarged size makes it harder for members to coordinate and collaborate without partisanship and legislative structures \citep{kirkland2014chamber, rush2013conclusion}. It also increases the potential number of veto players, decreasing the policymaking efficiency \citep{tsebelis2002veto}. Balancing these two incentives is crucial for the optimal legislative composition \citep{auriol2012optimal, taagepera1972size}.

However, the legislature size scholarship has overlooked two questions: first, does legislature size matter in contexts where the legislative bodies are not the pivotal decision-maker? And second, what is the ultimate effect of legislature size on welfare? On the one hand, legislature size's effects on welfare represent a significant gap in the political economy literature. It is likely generated by the predominance of the "law of 1/n" scholarship, which emphasized larger legislatures' overspending consequence. Since the seminal paper by \citet{Weingastetal1981}, 30 papers have systematically tested the effects of legislature size on government spending \citep{freire2021legislature}. Of these papers, only \citet{lewis2019legislature} investigates its effects on welfare, showing that larger legislatures have a negative welfare effect.\footnote{\citet{koppel2004public} also shows, using a repeated game where the proposal prerogative rotates in a legislature, that larger legislatures increase the chances of non-cooperative outcomes, lowering public goods provision.} \citet{frey2021legislature} analyses the Brazilian case after the 2009 legislature size change and finds a null effect in service provision from 2012 to 2016. \textbf{Yet, \citet{GilliganMatsusaka2001} finds that in the US legislature size is associated primarily with higher spending on geographically concentrated benefits, such as education and highways.} These results suggest that the legislature size and welfare nexus needs a dedicated theoretical and empirical assessment.

@@

Following the ruling of the Supreme Court, in March 2004 the Supreme Electoral Court established a series of population cutoffs for all municipal legislatures. Following the Brazilian Constitution, the Court specified that cities with up to one million residents should have between 9 and 21 legislators. The number of seats was allocated as follows. Each town starts with nine councilors, then adds one legislator for every 47,619 inhabitants until their councils reach 21 members. This threshold implies that cities with a population between 571,428 and one million should all have the same number of legislators, that is, 21 of them. Conversely, cities between one and four million inhabitants should have at least 33 councilors, and this number increases up to 41 members following the previous formula of one additional legislator per 47,619 inhabitants. \textbf{Additionally, Brazil’s formula for apportioning legislative seats (a combination of the Hara quota and the D’Hondt method) is an obstacle to small parties or coalitions attaining the electoral quotient that might give them a legislative seat. As a result, they often ally with larger coalitions so that they can reach the electoral quotient \citep[p. 68]{Ames2001}. Being a central political figure in the municipality, often the mayor is also a member of the most voted coalition.}

@@

We built two novel datasets to provide evidence for our mechanism. First, we ran a survey with former city councilors, asking how mayors consolidate their coalition support within the city council.\footnote{We provide further information about the city council survey in section A.14 of the Supplementary Materials.} Second, we collected 346,553 laws approved in 63 municipalities within ten thousand inhabitants away from the city council size thresholds. We hand-coded 3,466 laws into four categories: public goods, oversight, education and health care-related legislation, and other legislative duties. After hand-coding these laws, we used a Supporting Vector Machine (SVM) algorithm to classify the remainder laws. From all of the algorithms we tested, SVM achieved the highest performance.

@@

Municipalities work very similarly in terms of the incentives for legislative-executive bargaining. The stakes are lower, and the negotiations involve only one legislative branch. Still, in a system such as Brazil's, with more than thirty-five registered parties, mayors face substantial challenges to the support for their agendas. Having extra help in the council can tilt the bargaining towards cheaper governing, thus improving public goods provision. \textbf{Future research should also evaluate whether an extra-legislator is helping the mayor in her competition for state or federal transfers, as proposed by \citet{catalinac2020tournament}.}
